General analysis notebook for `forward` budget models.

### 2018-01-30 voltagebudget/analysis/ranked_sum_analysis.Rmd

```{r, message=FALSE, fig.width=3, fig.height=1}
# Load min, max V_free and neighbors
exp_name <- "exp18"
freq = "30"

@@

rank <- "1"
name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

# rank <- "2"
# name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
# rdata <- read_csv(paste(name, sep=""))
# rdata$rank <- rep(rank, nrow(rdata))
# ranked <- rbind(ranked, rdata)

rank <- "3"
name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

rank <- "50"
name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

# rank <- "49"
# name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
# rdata <- read_csv(paste(name, sep=""))
# rdata$rank <- rep(rank, nrow(rdata))
# ranked <- rbind(ranked, rdata)

rank <- "48"
name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

>>>>

```{r, message=FALSE, fig.width=3, fig.height=1}
# Load min, max V_free and neighbors
exp_name <- "exp29"
freq = "8"

@@

rank <- "1"
name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(name)
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

rank <- "2"
name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

rank <- "3"
name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

rank <- "50"
name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

rank <- "49"
name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

rank <- "48"
name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)
